Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2021-02-19 summary.Rmd
fixed some of the wording for theorem 5

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Sparse Subspace Clustering using LASSO \cite{pmlr-v28-wang13}.}
  \KwData{Adjacency matrix $A$, number of communities $K$, 
  hyperparameter $\lambda$}
  \KwResult{Community assignments $1, ..., K$}
    Find $Z$, the ASE of $A$ using the $K (K + 1) / 2$ most positive 
    and the $K (K - 1) / 2$ most negative eigenvalues and eigenvectors of 
    $A$.\;
    \For {$i = 1, ..., n$} {
      Assign $z_i^\top$ as the $i^{th}$ row of $Z$. 
      Assign $Z_{-i} = \begin{bmatrix} 
      z_1 & \cdots & z_{i-1} & z_{i+1} & \cdots & z_n \end{bmatrix}^\top$.\;
      Solve the LASSO problem 
      $c_i = \arg\min_{\beta_i} 
      \frac{1}{2} ||z_i - Z_{-i} \beta_i||_2^2 + \lambda ||\beta_i||_1$.\;
      Assign $\tilde{c}_i = \begin{bmatrix} 
      c_i^{(1)} & \cdots & c_i^{(i-1)} & 0 & c_i^{(i)} & \cdots & c_i^{(n-1)}
      \end{bmatrix}^\top$ such that the superscript is the index of 
      $\tilde{c}_i$.\;
    }
    Assign 
    $C = \begin{bmatrix} \tilde{c}_1 & \cdots & \tilde{c}_n \end{bmatrix}$.\;
    Compute $B = |C| + |C^\top|$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected subgraphs (e.g., using edge 
    thresholding or spectral clustering).\;
    Map each partition to the community labels $1, ..., K$. 
\end{algorithm}

**Theorem 5**. Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$. Let $Z_n$ be the ASE of 
$P_n$, and let $Z_n^{(k)}$ correspond to the embedding points that correspond 
to the $k$^th^ block. Let $\hat{Z}_n$ be the ASE of $A_n$ and $\hat{Z}_n^{(k)}$ 
be the corresponding $k$^th^ block. If $r(Z_n^{(k)})$, the inradius of 
$Z_n^{(k)}$ (as defined by \citet{soltanolkotabi2012}), is positive for each 
$k$, then the SSC detection property holds for $\hat{Z}_n$ with probability 1 
as $n \to \infty$.

>>>>

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Sparse Subspace Clustering using LASSO \cite{pmlr-v28-wang13}.}
  \KwData{Adjacency matrix $A$, number of communities $K$, 
  hyperparameter $\lambda$}
  \KwResult{Community assignments $1, ..., K$}
    Find $Z$, the ASE of $A$ using the $K (K + 1) / 2$ most positive 
    and the $K (K - 1) / 2$ most negative eigenvalues and eigenvectors of 
    $A$.\;
    \For {$i = 1, ..., n$} {
      Assign $z_i^\top$ as the $i^{th}$ row of $Z$. 
      Assign $Z_{-i} = \begin{bmatrix} 
      z_1 & \cdots & z_{i-1} & z_{i+1} & \cdots & z_n \end{bmatrix}^\top$.\;
      Solve the LASSO problem 
      $c_i = \arg\min_{\beta_i} 
      \frac{1}{2} ||z_i - Z_{-i} \beta_i||_2^2 + \lambda ||\beta_i||_1$.\;
      Assign $\tilde{c}_i = \begin{bmatrix} 
      c_i^{(1)} & \cdots & c_i^{(i-1)} & 0 & c_i^{(i)} & \cdots & c_i^{(n-1)}
      \end{bmatrix}^\top$ such that the superscript is the index of 
      $\tilde{c}_i$.\;
    }
    Assign 
    $C = \begin{bmatrix} \tilde{c}_1 & \cdots & \tilde{c}_n \end{bmatrix}$.\;
    Compute the affinity matrix $B = |C| + |C^\top|$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected subgraphs (e.g., using edge 
    thresholding or spectral clustering).\;
    Map each partition to the community labels $1, ..., K$. 
\end{algorithm}

**Theorem 5**. Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$. Let $Z_n$ be the ASE of 
$P_n$, and let $Z_n^{(k)}$ correspond to the embedding points that correspond 
to the $k$^th^ community. Let $\hat{Z}_n$ be the ASE of $A_n$ and $\hat{Z}_n^{(k)}$ 
be the corresponding $k$^th^ block. Let $\hat{B}_n$ be the affinity matrix in the SSC algorithm with input $\hat{Z}_n$ such that $\hat{B}_n^{(ij)}$ is the $ij$^th^ element of $\hat{B}_n$. If $r(Z_n^{(k)})$, the inradius of $Z_n^{(k)}$ (as defined by \citet{soltanolkotabi2012}), is positive for each $k$, then $\hat{B}_n^{(ij)} \stackrel{p}{\to} 0$ $\forall i, j$ in different communities.
